Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-07 SupportingInformation.Rmd
minor plotting change

```{r overwritting_plots_asym_cop,echo=F,results="hide"}
pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_neg0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.3,0))
pop<-ans_b_neg0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()
```

>>>>

```{r overwritting_plots_asym_cop,echo=F,results="hide"}
pdf("./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.1_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.1$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.1$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()

pdf("./Results/asym_sens_results/a_0.2_b_-0.9_r_0.8_asym_sens.pdf",height=3,width=6)
op<-par(mfrow=c(1,2),mar=c(3.5,4,1,1),mgp=c(2.2,0.5,0))
pop<-ans_b_neg0.9$pop
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"A",cex=2)
pop<-ans_b_neg0.9$pop_d
plot(pop[,1],pop[,2],xlab=expression(paste(E[1])), ylab=expression(paste(E[2])),cex.lab=1.5,cex.axis=1,col="grey",pch=20,cex=0.6)
text(0.1,0.95,"B",cex=2)
par(op)
dev.off()
```
